### 2016-07-08 draft.tex
Trivial edit.
Added computational stuff

	\section{Computational details}
	In every case calculating the bound requires integrating an expression involving the long and complicated Bremsstrahlung amplitude, which unfortunately could not be done analytically without making unjustified approximations. The integration was consequently performed numerically using the Monte Carlo routines provided by the Cuba library. The complexity of the integration was such that errors remained relatively large even with highest practicable number of samples. 
	\section{Results}
	\section{Discussion/Conclusion}

>>>>

	\section{Computational details}
	In every case calculating the bound requires integrating an expression involving the long and complicated Bremsstrahlung amplitude, which unfortunately could not be done analytically without making unjustified approximations. The integration was consequently performed numerically using the Monte Carlo routines provided by the Cuba library. Employing kinematic relations did not seem to reduce the complexity of the problem, so in the interests of reducing the number of possible mistakes the kinematics were done by brute force. We integrated over the entire phase space explicitly in terms of the eleven variables of $ \vec{p_1}, \vec{p_2}, \vec{p_3}, \hat{q_a} $, then fixed $ p_4 $ using the 3-momentum part of the delta-function and used an unpleasantly complicated equation obtained from the energy delta-function to fix the remaining one free momentum amplitude - in our case we chose this to be $ q_a $, the momentum of the emitted boson. At each step points resulting in unphysical configurations were discarded, and the remaining points were then plugged in to the appropriate amplitude, and then that result used as the integrand. The numerical integration routine used was the \textit{Suave} method provided by CUBA, which combines importance sampling and adaptive subdivision; this method seemed to provide the best compromise between computation time and error.

	Once the integration is complete the calculation of the trapping and streaming limits is a straightforward application of the equations previously derived, and proceeded as outlined above. The decay limit is somewhat harder, since $ \epsilon $ appears on both sides of the equation. Again we employed an unsubtle approach to solving the problem: $ \epsilon $ was set to an arbitrary value where the constraint was satisfied, and then iteratively reduced until the constraint was no longer satisfied. This obviously introduces another source of error, but with a sufficiently small interval in $ \epsilon $ this is negligible. The one further slight complication is that at after a certain value of $ M_A $ the decay limit rapidly goes to zero, at which point the procedure was terminated.

	We then scanned over the desired range of values for $ M_A $ and output the three limits - trapping, decay, and streaming - at each point. The complexity of the integration was such that errors remained relatively large even with highest practicable number of samples.

	\section{Results}
	\section{Discussion/Conclusion}
